Initial Analysis

### 2020-08-05 Scripts/Initial_Analysis.Rmd
misc.

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    # st_transform(crs = 4326) %>% # 4326
    st_transform(crs = "+proj=eck4") %>%
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)

@@

# Dataset to match all SAU names
matching_names <- my_path("G"),"Spatial/SAU", "matching_names.csv", read = T)

@@

# Load Transbonudary results
Raw_Results_Trans <- my_path("R","EEZ","Raw_Results_Trans.xlsx", read = T)
Clean_Results_Trans <- Raw_Results_Trans %>% 
  CleanResults(.,clean_names) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(matching_names,
            by = "sf_eez_name") %>% 
  rename(eez_name = sf_eez_name,
         fishing_entity = sau_fishing_entity)

# New data produced by Vicky to compare with Teh and Sumaila
Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  left_join(matchig_names,
            by = "iso_a3") %>% 
  distinct(iso_a3,.keep_all = TRUE) %>% 
  rename(fishing_entity = sau_fishing_entity)

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- EEZ_Area %>% 
  left_join(matchig_names,
            by = "eez_id") %>% 
  group_by(fishing_entity = sau_fishing_entity,fishing_entity_id) %>% 
  summarise(Size_Entity = sum(Size_EEZ))

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
  select(-geometry) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(sf_eez_name=territory) %>% 
  left_join(clean_names) %>% 
  rename(eez_name = sau_eez_name)
```

@@

# number of eezs
length(unique(World_sf$eez_name))

# Number of coastal territories
length(unique(Clean_sau_eez_fes$fishing_entity))

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
      area_index > Max_AI |
      model_index < MI
  ) %>% 
  # Needed to correct for names
  # select(-fishing_entity) %>% 
  # left_join(Clean_sau_eez_fes,
            # by = "eez_name") %>% 
  # Remove Countries that share with other countries
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  )

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(eez_name, eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  ungroup() %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')
                    )
  )

>>>>

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    # st_transform(crs = 4326) %>% # 4326
    st_transform(crs = "+proj=eck4") %>%
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity_id") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!fishing_entity_id %in% World_sf_si_land$fishing_entity_id)

@@

# Dataset to match all SAU names
matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)

@@

# Load Transbonudary results
Raw_Results_Trans <- my_path("R","EEZ","Raw_Results_Trans.xlsx", read = T)

Clean_Results_Trans <- Raw_Results_Trans %>% 
  CleanResults(.,matching_names) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(matching_names,
            by = "sf_eez_name") %>% 
  rename(eez_name = sf_eez_name,
         fishing_entity = sau_fishing_entity)

# New data produced by Vicky to compare with Teh and Sumaila
# Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
    # rename(sau_fishing_entity = name_long) %>%
  left_join(matching_names,
            by = "iso_a3") %>% 
  distinct(iso_a3,.keep_all = TRUE) %>% 
  rename(fishing_entity = sau_fishing_entity)

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- EEZ_Area %>% 
  left_join(matching_names,
            by = "eez_id") %>% 
  group_by(fishing_entity = sau_fishing_entity,fishing_entity_id) %>% 
  summarise(Size_Entity = sum(Size_EEZ))

# Regional UN-sub region area
Regional_Area <- Entity_Area %>% 
  left_join(UN_Regions) %>% 
  group_by(sub_region) %>% 
  summarise(size_region = sum(Size_Entity,na.rm=T))%>% 
  arrange(size_region)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(sf_eez_name=territory) %>% 
  left_join(matching_names) %>% 
  rename(eez_name = sau_eez_name)
```

@@

# number of eezs
length(unique(World_sf$eez_name))
# Number of coastal territories
length(unique(matching_names$fishing_entity))

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
      area_index > Max_AI |
      model_index < MI
  ) %>% 
  # Remove Countries that share with other countries
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  )

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name, eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  ungroup() %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')
                    )
  )
